Tidal field anisotropy as a tracer of cosmic voids

### 2015-02-11 cosmic_voids.tex
revised section 3

\begin{abstract}
Finding and characterizing underdense regions (voids) in the large
scale structure of the Universe is an important task in cosmological
studies.  
In this paper we present a novel approach to find voids in
cosmological simulations.  
Our approach is based on algorithms that use the tidal and the
velocity shear tensors to locally define the cosmic web.
Voids are identified using the fractional anisotropy (FA) computed
from the eigenvalues of each web scheme. 
We define the void boundaries using a watershed transform based on the
local minima of the FA and its boundaries as the regions where the FA
is maximized.
This void identification technique does not have any free parameters
and does not make any assumption on the shape or structure of the
voids.  
We test the method on the Bolshoi simulation and report on the density
and velocity profiles for the voids found using this new scheme. 
We find that...
\end{abstract}

@@

@@

In left panels of Fig. \ref{fig:FA_field} we show the FA field for both 
web schemes over a slide of the simulation. 
From this Figure we can observe that both, voids and knots, display a highly 
isotropic expanding dynamic at their centres, becoming gradually more
anisotropic at outer regions. 
On the other hand the filamentary structure is traced by high FA
values. These characteristics are the key to use the FA as a tracer of
cosmic voids.

%.........................................................................
%FIGURE 1: FA and vissual impression
\begin{figure*}
  \includegraphics[trim = 16mm 8mm 5mm 12mm, clip, keepaspectratio=true,
  width=0.73\textheight]{cosmicweb_FA_Tweb.pdf}
  \includegraphics[trim = 16mm 8mm 5mm 12mm, clip, keepaspectratio=true,
  width=0.73\textheight]{cosmicweb_FA_Vweb.pdf}
  \caption{Left colum. Visual impression of the 
  FA field over a slide of the simulation for each web scheme (T-web, upper 
  panels. V-web, middle panels). 
  Middle column. Components of the Cosmic Web using $\lambda_{th}$
  values that put an upper bound of $FA=0.95$ to voids. Voids
  corresponds with white, sheets to gray, filaments to dark gray and
  knots with black regions. 
  Right column. Sketches the distribution of the catalogued voids by
  our method.}
  \label{fig:FA_field}
\end{figure*}
%.........................................................................

@@

  \includegraphics[trim = 2mm 2mm 5mm 10mm, clip, keepaspectratio=true,
  width=0.3\textheight]{FA_L1.pdf}
  \includegraphics[trim = 2mm 2mm 5mm 10mm, clip, keepaspectratio=true,
  width=0.3\textheight]{delta_L1.pdf}

@@

Voids are regions where $\lambda_3\leq\lambda_2\leq
\lambda_1\leq\lambda_{th}$. 
This implies that a void is completely fixed by the relative strength
of the $\lambda_1$ eigenvalue with respect to the $\lambda_{th}$.   
As we  increase/decrease the threshold value $\lambda_{th}$, voids
increase/decrease progressively through contours of
increasing/decreasing $\lambda_1$.

Voids are thus characterized by low values of both FA and
$\lambda_1$. 
In Fig. \ref{fig:L1_correlations} we show that the these two values
are indeed closely correlated.  
The left panel shows the correlation between $\lambda_1$ and $FA$ for
all the grid cells in the simulation while the right panel shows the
correlation between $\lambda_1$ and the local overdensity $\delta$.  
This shows that the overdensity has a large scatter at fixed
$\lambda_1$.

@@

Once established the FA as a good tracer of voids, the next step is to
find individuals voids in the overall distribution. For this purpose, we
use the \textit{watershed transform algorithm} \citep{Beucher79,Beucher93}, 
in which a void is identified as the catching basin of a local minimum of
the FA. The use of this algorithm is advantageous as it is parameter-free 
and does not require any assumption on the shape and morphology of voids.

Previous implementations of this technique as those of \citet{Platen07,
Neyrinck08} have shown remarkable results regarding voids finding, however
they use the density field instead of the FA field. On the other hand, we 
use a \textit{cloud-in-cell} (\texttt{CIC}) algorithm on a Cartesian mesh for 
estimating the density and tensor fields, instead of the more sophisticated 
\textit{Delaunay tessellation for field estimator} (\texttt{DTFE}) technique 
\citep{Schaap00}, but our implementation of the watershed transform should 
not be significantly affected as we are interested in low density regions 
where the \texttt{CIC} gives similar estimations.

As suggested by \citet{Platen07} and references therein, it is necessary to
apply a threshold merger in order to reduce spurious features and to avoid 
void hierarchization. A natural choice is a threshold of $\delta = -0.8$, 
which means that any ridge between two voids with density below that value
would be removed and the respective voids merged. As we are working with the
FA, the equivalent threshold according to Fig. \ref{fig:L1_correlations} is
$FA = 0.65$. In right panels of Fig. \ref{fig:FA_field} we show the resulting
catalogues of voids for both schemes.

%Once set the optimal thresholds for the web schemes, we proceed in Fig. 
%\ref{fig:FAShapeness} to sample the FA and the prolateness for a random 
%sample of cells previously classified into one of the four
%environments.

%The prolateness is introduced here for differentiating sheets and filaments
%featuring high FA values. 
%In order to illustrate the underlying local 
%dynamics sampled by the cells, we also sketch different spheroidal 
%geometries according to the relative strength of each eigenvalue, and 
%then, we associate them to different ranges of the FA and the prolateness.

%From this, we conclude sheets display very anisotropic distributions, 
%namely above $FA=0.95$. They are also biased towards oblate geometries, 
%however there are some elongated sheets as well. Filaments are not as 
%anisotropic as sheets, ranging from middle up to high FA values. They 
%exhibit prolate geometries, but a considerable fraction of them are biased 
%towards slightly more oblate values. Voids and knots are the only 
%environments featuring with low FA values, thus indicating very isotropic 
%expanding/collapsing dynamics at their centres. However, voids span over 
%a very wide range of FA and geometries, whereas knots only span over low 
%to middle FA values and display a biased oblate geometry.

>>>>

\begin{abstract}
Finding and characterizing underdense regions (voids) in the large
scale structure of the Universe is an important task in cosmological
studies.  
In this paper we present a new algorithm to find voids in
cosmological simulations.  
Our approach is based on algorithms that use the tidal and the
velocity shear tensors to locally define the cosmic web.
Voids are identified using the fractional anisotropy (FA) computed
from the eigenvalues of each web scheme. 
We define the void boundaries using a watershed transform based on the
local minima of the FA and its boundaries as the regions where the FA
is maximized.
This void identification technique does not have any free parameters
and does not make any assumption on the shape or structure of the
voids.  
We test the method on the Bolshoi simulation and report on the density
and velocity profiles for the voids found using this new scheme. 
We find that...
\end{abstract}

@@

%.........................................................................
%FIGURE 1: FA and vissual impression
\begin{figure*}
  \includegraphics[trim = 16mm 8mm 5mm 12mm, clip, keepaspectratio=true,
  width=0.73\textheight]{cosmicweb_FA_Tweb.pdf}
  \includegraphics[trim = 16mm 8mm 5mm 12mm, clip, keepaspectratio=true,
  width=0.73\textheight]{cosmicweb_FA_Vweb.pdf}
  \caption{Left colum. Visual impression of the 
  Fractional Anisotropy field over a slide of the simulation for each
  web scheme (T-Web is up. V-Web is down).  
  Middle column. Cosmic Web identification. Voids
  are white, sheets are light gray, filaments are dark gray and
  knots are black.
  Right column. Colors are voids identified by our Fractional
  Anisotropy method.}
  \label{fig:FA_field}
\end{figure*}
%.........................................................................

@@

In the left and middle panels of Figure \ref{fig:FA_field} we show the
FA field and web classification for both  web schemes over a slice of
an N-body simulation (described in Section \ref{sec:simulations}). 
Comparing these two panels we see that voids and knots (white
and black in the middle panel of Figure 1) display low FA values at
their  centres, becoming gradually more anisotropic at outer regions.  
On the other hand the filamentary structure (grey in the middle panel
of Figure 1) is traced by high FA values.  
These characteristics are key to use the FA as a tracer of cosmic voids.

@@

  \includegraphics[trim = 2mm 2mm 5mm 10mm, clip, keepaspectratio=true,
  width=0.3\textheight]{delta_L1.pdf}  
  \includegraphics[trim = 2mm 2mm 5mm 10mm, clip, keepaspectratio=true,
  width=0.3\textheight]{FA_L1.pdf}

@@

Voids are regions where $\lambda_3\leq\lambda_2\leq
\lambda_1\leq\lambda_{th}$. 
This implies that a void is completely fixed by the relative strength
of the $\lambda_1$ eigenvalue with respect to the threshold.   
As we increase/decrease the threshold value $\lambda_{th}$, voids
increase/decrease progressively through contours of
increasing/decreasing $\lambda_1$.  
Voids are thus characterized by low values of both FA and
$\lambda_1$.

In Fig. \ref{fig:L1_correlations} we show that the these two values
are indeed closely correlated.  
The left panel shows the correlation between $\lambda_1$ and $FA$ for
all the grid cells in the simulation while the right panel shows the
correlation between $\lambda_1$ and the local overdensity $\delta$.  
This shows that the overdensity has a large scatter at fixed
$\lambda_1$.

@@

The previous section shows that FA is a good void tracer, but it does
not automatically suggest how to define the boundary of individual
voids.
For this purpose, we
use the \textit{watershed transform algorithm}
\citep{Beucher79,Beucher93} to identify a void as the basin of FA
local minimum. 
The advantage of this definition is that we can
now forget about the free parameter $\lambda_{th}$. 
Additionally, this algorithm does not require any assumption on the
shape and/or morphology of the tentative voids.

The watershed technique has been already implemented to find voids \citet{Platen07,
Neyrinck08} however it used the density field instead of the FA
field as we suggest in this paper. 
Another difference with respect to other void finding implementations
is that we estimate all relevant quantities on a Cartesian mesh of fixed cell
size, while it other works use an adaptive Delaunay tessellation
\citep{Schaap00}. 
However from the analysis of our results this different does not seem
to introduce supurious results, at least with the mass resolution we
have in the N-body simulation.

This watershed algorithm still needs a threshold value to reduce
spurious features and to avoid void hierarchization.  
If the density field is used, a typical threshold is
$\delta = -0.8$ \citep{Platen07},  which means that any ridge between
two voids with overdensity below that value is removed to merge the
respective voids. 
In our case we have to find a corresponding FA value
to define this threshold.

In Figure \ref{fig:L1_correlations} we find the correlations of
the eigenvalue $\lambda_1$ with he matter overdensity (left panel) and
the FA (right panel).
We can use this information to find the FA threshold. 
From the left panel we see that an underdensity of $\delta=-0.8$ is
correspond to values of $\lambda_1=0.0$, regardless of the web-finding
scheme.
From the second panel we have a very tight correlation of $\lambda_1$
with the FA, indicating that in turn $\lambda_1=0.0$ corresponds to a
FA=$0.65$ which is the value that we have used to remove ridges.

The right column in Figure \ref{fig:FA_field} shows all the voids that
have been identified using the watershed algorithm on the FA field.
